linearGR_Models

### 2018-06-20 manuscriptAnalysis/linearGR_ModelsMap_BKT.Rmd
chagned grIndRE structure

@@

bySpecies <- bySpecies %>%
     #  mutate( model1 =  map(data, mod[[1]]) ) %>%
     #  mutate( model2 =  map(data, mod[[2]]) ) %>%
     #  mutate( model3 =  map(data, mod[[3]]) ) %>%
     #  mutate( model4 =  map(data, mod[[4]]) ) %>%
     #  mutate( model5 =  map(data, mod[[5]]) ) %>%
     #  mutate( model6 =  map(data, mod[[6]]) ) %>%
     #  mutate( model7 =  map(data, mod[[7]]) ) %>%
     # mutate( model8 =  map(data, mod[[8]]) ) %>%
     # mutate( model9 =  map(data, mod[[9]]) ) %>%
     # mutate( model10 = map(data, mod[[10]]) ) %>%
     # mutate( model11 = map(data, mod[[11]]) ) %>%
     # mutate( model12 = map(data, mod[[12]]) ) %>%
     # mutate( model13 = map(data, mod[[13]]) ) %>%
     #  mutate( model14 = map(data, mod[[14]]) ) %>%
     #  mutate( model15 = map(data, mod[[15]]) ) %>%
     #  mutate( model16 = map(data, mod[[16]]) ) %>%
     #  mutate( model17 = map(data, mod[[17]]) ) %>%
     #  mutate( model18 = map(data, mod[[18]]) ) %>%
     # mutate( model19 = map(data, mod[[19]]) ) %>%
     #  mutate( model20 = map(data, mod[[20]]) )# %>%
      mutate( model21 = map(data, mod[[21]])) %>%
      mutate( model22 = map(data, mod[[22]])) #%>%
    #  mutate( model23 = map(data, mod[[23]]))
```

```{r}
#2 or 5 fish have lengthByYear = NA whcih gives warining of diff # of observations when include mod with lengthByYear

o <- bySpecies
b <- AIC(o$model1[[1]],
         o$model2[[1]],
           o$model3[[1]],
           o$model4[[1]],
           o$model5[[1]],
           o$model6[[1]],
           o$model7[[1]],
           o$model8[[1]],
           o$model9[[1]],
           o$model10[[1]],
           o$model11[[1]],
           o$model12[[1]],
           o$model13[[1]],
            o$model14[[1]],
            o$model15[[1]],
            o$model16[[1]],
            o$model17[[1]],
            o$model18[[1]],
           o$model19[[1]],
           o$model20[[1]],
           o$model21[[1]],
           o$model22[[1]],
          o$model23[[1]]
         ) %>% rownames_to_column() %>% arrange(AIC) #bkt
n <- AIC(o$model1[[2]],
         o$model2[[2]],
           o$model3[[2]],
           o$model4[[2]],
           o$model5[[2]],
           o$model6[[2]],
           o$model7[[2]],
           o$model8[[2]],
           o$model9[[2]],
           o$model10[[2]],
           o$model11[[2]],
           o$model12[[2]],
           o$model13[[2]],
            o$model14[[2]],
            o$model15[[2]],
            o$model16[[2]],
            o$model17[[2]],
            o$model18[[2]],
           o$model19[[2]],
           o$model20[[2]],
           o$model21[[2]],
           o$model22[[2]],
           o$model23[[2]]
         ) %>% rownames_to_column() %>% arrange(AIC)#bnt
a <- AIC(o$model1[[3]],
         o$model2[[3]],
           o$model3[[3]],
           o$model4[[3]],
           o$model5[[3]],
           o$model6[[3]],
           o$model7[[3]],
           o$model8[[3]],
           o$model9[[3]],
           o$model10[[3]],
           o$model11[[3]],
           o$model12[[3]],
           o$model13[[3]],
            o$model14[[3]],
            o$model15[[3]],
            o$model16[[3]],
            o$model17[[3]],
            o$model18[[3]],
            o$model19[[3]],
           o$model20[[3]],
           o$model21[[3]],
           o$model22[[3]],
          o$model23[[3]]
          ) %>% rownames_to_column() %>% arrange(AIC)#ats

@@

>>>>

```{r}
# add squared terms back in to good model for ats? NO

mod[[24]] <- function(df) {
    print(c('mod = 24' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd +
                   isYOY * river * season * cATSStd2 +
                   isYOY * river * season * tempStd2 +

mod[[25]] <- function(df) {
    print(c('mod = 25' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd +
                   isYOY * river * season * cATSStd2 +

                   isYOY * river * season * flowStd2 +
                   (1|ind) + (1|season), data = df ) }

mod[[26]] <- function(df) {
    print(c('mod = 26' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd +
                   isYOY * river * season * cATSStd2 +
                   isYOY * river * season * tempStd2 +
                   isYOY * river * season * flowStd2 +
                   (1|ind) + (1|season), data = df ) }
```

          rowname  df       AIC      rowname.1 df.1     AIC.1      rowname.2 df.2     AIC.2
1  o$model17[[1]] 272 -24796.58 o$model18[[2]]  122 -11217.98 o$model11[[3]]   80 -29379.29
2  o$model18[[1]] 241 -24795.12 o$model16[[2]]  122 -11211.56 o$model15[[3]]   59 -28755.46
3  o$model16[[1]] 249 -24778.30 o$model17[[2]]  136 -11207.54 o$model24[[3]]   66 -28732.88
4  o$model14[[1]] 218 -24767.67 o$model12[[2]]   80 -11203.21 o$model26[[3]]   73 -28728.16
5  o$model19[[1]] 249 -24730.67 o$model22[[2]]  136 -11193.90 o$model25[[3]]   66 -28722.50
6  o$model20[[1]] 218 -24727.16 o$model20[[2]]  108 -11169.43 o$model22[[3]]   73 -28459.70
7  o$model21[[1]] 272 -24699.83 o$model13[[2]]  108 -11167.05 o$model23[[3]]   80 -28405.91
8  o$model13[[1]] 226 -24689.16  o$model8[[2]]   66 -11166.73 o$model16[[3]]   66 -28318.31
9  o$model10[[1]] 195 -24650.05 o$model21[[2]]  136 -11152.36 o$model17[[3]]   73 -28313.67
10 o$model22[[1]] 272 -24608.90 o$model19[[2]]  122 -11146.57 o$model14[[3]]   59 -28310.73
11 o$model15[[1]] 210 -24589.74 o$model14[[2]]  108 -11140.80 o$model13[[3]]   59 -28306.10
12 o$model23[[1]] 303 -24567.09 o$model23[[2]]  149 -11139.31 o$model19[[3]]   66 -28282.69
13 o$model25[[1]] 241 -24463.80  o$model7[[2]]   66 -11129.29 o$model18[[3]]   66 -28267.13
14 o$model24[[1]] 241 -24462.46 o$model10[[2]]   94 -11119.43 o$model21[[3]]   73 -28244.31
15 o$model26[[1]] 272 -24413.64  o$model9[[2]]   66 -11108.18 o$model10[[3]]   52 -28077.66
16  o$model7[[1]] 139 -24336.63  o$model1[[2]]   59 -11091.02 o$model20[[3]]   59 -28017.53
17 o$model12[[1]] 155 -24316.48  o$model6[[2]]   73 -11085.12 o$model12[[3]]   52 -27717.41
18 o$model11[[1]] 187 -24259.03  o$model2[[2]]   60 -11074.95  o$model7[[3]]   38 -27339.65
19  o$model1[[1]] 131 -24064.23 o$model11[[2]]  108 -11049.99  o$model3[[3]]   45 -27221.73
20  o$model2[[1]] 132 -24049.02  o$model5[[2]]   73 -11045.37  o$model4[[3]]   52 -27214.79
21  o$model8[[1]] 139 -24045.93 o$model25[[2]]  122 -11045.32  o$model6[[3]]   38 -26849.65
22  o$model9[[1]] 139 -24007.57 o$model15[[2]]  108 -11030.68  o$model8[[3]]   38 -26845.97
23  o$model5[[1]] 163 -23950.60  o$model3[[2]]   87 -11011.79  o$model5[[3]]   38 -26825.20
24  o$model6[[1]] 163 -23862.94 o$model26[[2]]  136 -10980.93  o$model9[[3]]   38 -26695.14
25  o$model4[[1]] 226 -23856.48 o$model24[[2]]  122 -10963.97  o$model1[[3]]   31 -26673.04
26  o$model3[[1]] 195 -23825.07  o$model4[[2]]  101 -10916.61  o$model2[[3]]   32 -26662.86

@@

bySpecies <- bySpecies %>%
       mutate( model1 =  map(data, mod[[1]]) ) %>%
       mutate( model2 =  map(data, mod[[2]]) ) %>%
       mutate( model3 =  map(data, mod[[3]]) ) %>%
       mutate( model4 =  map(data, mod[[4]]) ) %>%
       mutate( model5 =  map(data, mod[[5]]) ) %>%
       mutate( model6 =  map(data, mod[[6]]) ) %>%
       mutate( model7 =  map(data, mod[[7]]) ) %>%
       mutate( model8 =  map(data, mod[[8]]) ) %>%
       mutate( model9 =  map(data, mod[[9]]) ) %>%
       mutate( model10 = map(data, mod[[10]]) ) %>%
       mutate( model11 = map(data, mod[[11]]) ) %>%
       mutate( model12 = map(data, mod[[12]]) ) %>%
       mutate( model13 = map(data, mod[[13]]) ) %>%
       mutate( model14 = map(data, mod[[14]]) ) %>%
       mutate( model15 = map(data, mod[[15]]) ) %>%
       mutate( model16 = map(data, mod[[16]]) ) %>%
       mutate( model17 = map(data, mod[[17]]) ) %>%
       mutate( model18 = map(data, mod[[18]]) ) %>%
       mutate( model19 = map(data, mod[[19]]) ) %>%
       mutate( model20 = map(data, mod[[20]]) ) %>%
       mutate( model21 = map(data, mod[[21]]) ) %>%
       mutate( model22 = map(data, mod[[22]]) ) %>%
       mutate( model23 = map(data, mod[[23]]) ) %>%
       mutate( model24 = map(data, mod[[24]]) ) %>%
       mutate( model25 = map(data, mod[[25]]) ) %>%
       mutate( model26 = map(data, mod[[26]]) )
```

> bySpecies$model18[[1]]
Linear mixed model fit by REML ['lmerMod']
Formula: grLength ~ isYOY * river * season * tempStd * flowStd + isYOY *  
    river * season * cBKTStd + isYOY * river * season * cBNTStd +      isYOY * season * cATSStd + isYOY * river * season * cBNTStd2 +  
    isYOY * river * season * cBNTStd * cBKTStd + (1 | ind) +      (1 | season)
   Data: df
REML criterion at convergence: -25277.12
Random effects:
 Groups   Name        Std.Dev.
 ind      (Intercept) 0.02184 
 season   (Intercept) 0.04763 
 Residual             0.06008 
Number of obs: 9967, groups:  ind, 5731; season, 4

```{r}
#2 or 5 fish have lengthByYear = NA whcih gives warning of diff # of observations when include mod with lengthByYear

o <- bySpecies
b <- AIC(o$model1[[1]],
         o$model2[[1]],
           o$model3[[1]],
           o$model4[[1]],
           o$model5[[1]],
           o$model6[[1]],
           o$model7[[1]],
           o$model8[[1]],
           o$model9[[1]],
           o$model10[[1]],
           o$model11[[1]],
           o$model12[[1]],
           o$model13[[1]],
            o$model14[[1]],
            o$model15[[1]],
            o$model16[[1]],
            o$model17[[1]],
            o$model18[[1]],
           o$model19[[1]],
           o$model20[[1]],
           o$model21[[1]],
           o$model22[[1]],
          o$model23[[1]],
           o$model24[[1]],
           o$model25[[1]],
          o$model26[[1]]
         ) %>% rownames_to_column() %>% arrange(AIC) #bkt
n <- AIC(o$model1[[2]],
         o$model2[[2]],
           o$model3[[2]],
           o$model4[[2]],
           o$model5[[2]],
           o$model6[[2]],
           o$model7[[2]],
           o$model8[[2]],
           o$model9[[2]],
           o$model10[[2]],
           o$model11[[2]],
           o$model12[[2]],
           o$model13[[2]],
            o$model14[[2]],
            o$model15[[2]],
            o$model16[[2]],
            o$model17[[2]],
            o$model18[[2]],
           o$model19[[2]],
           o$model20[[2]],
           o$model21[[2]],
           o$model22[[2]],
           o$model23[[2]],
           o$model24[[2]],
           o$model25[[2]],
          o$model26[[2]]
         ) %>% rownames_to_column() %>% arrange(AIC)#bnt
a <- AIC(o$model1[[3]],
         o$model2[[3]],
           o$model3[[3]],
           o$model4[[3]],
           o$model5[[3]],
           o$model6[[3]],
           o$model7[[3]],
           o$model8[[3]],
           o$model9[[3]],
           o$model10[[3]],
           o$model11[[3]],
           o$model12[[3]],
           o$model13[[3]],
            o$model14[[3]],
            o$model15[[3]],
            o$model16[[3]],
            o$model17[[3]],
            o$model18[[3]],
            o$model19[[3]],
           o$model20[[3]],
           o$model21[[3]],
           o$model22[[3]],
          o$model23[[3]],
           o$model24[[3]],
           o$model25[[3]],
           o$model26[[3]]
          ) %>% rownames_to_column() %>% arrange(AIC)#ats

@@

#mod18
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd +
                   isYOY * river * season * cBKTStd2 +
                   isYOY * river * season * cBNTStd2 +
                   isYOY * river * season * cBNTStd * cBKTStd +
                   (1|ind) + (1|season), data = df ) }

```{r predict}

x <- seq(-1.5,1.5, by = 0.5)

xGrid <- expand.grid( isYOY=unique(d$isYOY), river=unique(d$river), season=unique(d$season), 
                      tempStd=x, flowStd=x, cBKTStd=x, cBNTStd=x, cATSStd=x,
                      ind=1867) %>%
                    mutate(cBKTStd2=cBKTStd^2, cBNTStd2=cBNTStd^2)

p <- predict( bySpecies$model18[[1]], xGrid )
xGridP <- cbind(xGrid,p)

tmp <- 
xGridP %>%
  group_by(isYOY,river,season) %>%
  summarize( meanP = round(mean(p),2) )

d %>%
  group_by(isYOY,river,season) %>%
#  summarize( meanP = round(mean(grLength, na.rm=T),2) )
  summarize( meanP = round(mean(flowStd, na.rm=T),2) ) %>%
  data.frame()

varsToPlot='flowStd'
isYOYGG=2
speciesGG='bkt'

#plotPredGrid <- function(xGridP, depVar, varsToPlot, isYOYGG, speciesGG) {
  all = c('tempStd','flowStd','cBKTStd','cBNTStd','cATSStd')

  #print(c(depVar,(as.name(depVar))))

 # if(length(varsToPlot) == 1) {
    notPlot <- NA
    notPlot[1] <- all[!(all %in% varsToPlot)][1]
    notPlot[2] <- all[!(all %in% varsToPlot)][2]
    notPlot[3] <- all[!(all %in% varsToPlot)][3]
    notPlot[4] <- all[!(all %in% varsToPlot)][4]
 #   notPlot[5] <- all[!(all %in% varsToPlot)][5]

 #   pGG <- p %>% filter(isYOY == isYOYGG, species == speciesGG, eval(as.name(notPlot[1])) == 0, eval(as.name(notPlot[2])) == 0, eval(as.name(notPlot[3])) == 0 ) %>%
#                 distinct(eval(as.name(varsToPlot[1])), iter, isYOY, river, species, season, .keep_all = TRUE)
    pGG <- xGridP %>% filter(isYOY == isYOYGG, eval(as.name(notPlot[1])) == 0, eval(as.name(notPlot[2])) == 0, eval(as.name(notPlot[3])) == 0,
                                          eval(as.name(notPlot[4])) == 0
                                        #, eval(as.name(notPlot[5])) == 0
                        ) %>%
      distinct(eval(as.name(varsToPlot[1])), isYOY, river, season, .keep_all = TRUE)

    ggOut <- 
      ggplot( pGG, aes( eval(as.name(varsToPlot[1])), p ) ) +
      geom_line( alpha=0.25 ) +
      theme_bw() +
      theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank()) +
      ggtitle(paste0('isYOY = ',isYOYGG,', species = ',speciesGG)) +
      geom_hline(yintercept = 0) +
    #  ylim(-0.25,1.33) +
      scale_x_continuous(varsToPlot[1]) +
      facet_grid(river~season)
ggOut
